### 2017-01-20 ms/hardcoded/ms.tex
added the paragraph in the intor about the oppotunistic attachment

1) Stability x persistence x community assembly - maybe the easiest part to put a theory. [H4]

2) Link assembly to restoration and ecosystem services, biodiversity crisis (input the former first paragraph). [H4]

@@

4) Paragraph that starts with "Understanding network assembly..." [H1 and H2]

@@

6) Maybe rephrase the last paragraph to more question driven statements?
We tested four theoretically motivated hypothesis exploring the process of community assembly using a eight-year
dataset of plant-pollinator network development following hedgerow
installment in the highly simplified and intensively managed
agricultural landscape of California's Central Valley. First,
we determine whether network assembly was punctuated by significant
reorganizations of interactions, and if assembling networks presented more change than the control, non-assembly hedgerows. We next tested whether the species
that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species, as would be expected by preferential
attachment. To further explore the mechanisms underlying the temporal
dynamics of the networks, also we examine patterns in the species and
interaction temporal turnover. Finally, we investigate whether
networks assemble toward predictable interaction patterns, and the
ramifications for the robustness of the networks.

>>>>

(First and second paragraphs as they are)

However, properties that enable a species to interact with a broad range of partners (\textit{i.e.}, generalized, high degree species), may switch partners depending on community context. The adaptive foraging theory predicts that there is a trade-off between foraging efficiency and resource availability; thus, if competing species are present, it is expected that there will be a decrease in niche overlap among species present in a given area. In this sense, when other, competing species are present, generalist species can explore different resources, switching their interaction partners. This alternative assembly mechanism can be described as an opportunistic attachment process. In the opportunistic attachment process generalist species, instead of being part of a persistent species' core, are actually the species that explore, opportunistically, the most available resources, that is, the resources that are being use the less. Thus, when you consider the assembly process in a time series, the most persistent species are also the ones that, through time, exhibit the highest degree, but are also the most variable in their network position at each particular time. Species may have multiple interaction partners, but only interact when opportunity arises.

@@

4) important to understand assembly because of habitat restoration and ecosystem services, biodiversity crisis (input the former first paragraph). [H4] (Paragraph that starts with "Understanding network assembly...")  [H1 and H2]

@@

6) Maybe rephrase the last paragraph to more question driven statements?

We tested four theoretically motivated hypothesis exploring the process of community assembly using a eight-year
dataset of plant-pollinator network development following hedgerow
installment in the highly simplified and intensively managed
agricultural landscape of California's Central Valley. First,
we determine whether network assembly was punctuated by significant
reorganizations of interactions, and if assembling networks presented more change than the control, non-assembly hedgerows. We next tested whether the species
that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species, as would be expected by preferential
attachment. To further explore the mechanisms underlying the temporal
dynamics of the networks, also we examine patterns in the species and
interaction temporal turnover. Finally, we investigate whether
networks assemble toward predictable interaction patterns, and the
ramifications for the robustness of the networks.
